---
title: "STATISTICS OF UDEMY COURSES"
author: "Mustafa ÇANDIR"
date: '2022-07-12'
output: pdf_document
---
##libraries
```{r}
library(ggplot2)
library(dplyr)
library(MASS)
library(AID)
library(car)
library(corrplot)
library(hrbrthemes)
```

##read data
```{r}
dataudemy <- read.csv("D:/github/stat 250 2nd time/udemy_courses.csv")

```

## plots for variables
#1
```{r}
dataudemy %>%
  ggplot( aes(x=price)) +
    geom_density(fill="yellow", 
                 color="blue", 
                 alpha=0.9)

```

#2
```{r}
tab2 <- as.data.frame(table(dataudemy$level))
tab2
barplot(height=tab2$Freq, 
        names=tab2$Var1, 
        col="blue",
        # horiz=F, 
        las=1,
        main = "Price in levels",
        ylab = "Price",
        xlab = "Levels")
```

#3
```{r}
 ggplot(data=dataudemy, 
             aes(x=price, 
                group=subject, 
                fill=subject)) +
    geom_density(adjust=1.2, 
                 alpha=0.5) 
```

#4
only numerics as simple table
```{r}
corr=round(cor(dataudemy[,c(5,6,7,8,10)]),3)
corr
```

# corelation matrix as a plot
```{r}
corrplot(corr, 
         type = "upper", 
         order = "hclust", 
         tl.col = "black", 
         tl.srt = 45)
```

#5
The most popular 3 courses
```{r}
asd<-dataudemy[order(dataudemy$num_subscribers,
                                  decreasing = TRUE),]

barplot(asdbar$num_subscribers[1:3],
        main="The most popular 3 courses",
        xlab="Courses",
        ylab="Number of Subscribers",
        names.arg = asd$course_title[1:3],
        cex.names=0.7,
        col="orange")
```

#6
```{r}
ggplot(dataudemy, 
       aes(x=num_subscribers, 
                      y=num_lectures)) + 
  geom_point() + 
  stat_smooth(method = lm)
  
ggplot(dataudemy, 
       aes(x=price, 
           y=num_lectures)) + 
  geom_point()+ 
  stat_smooth(method = lm)
  
ggplot(dataudemy, 
       aes(x=num_reviews, 
           y=num_lectures)) + 
  geom_point() 

ggplot(dataudemy, 
       aes(x=content_duration, 
           y=num_lectures)) + 
  geom_point() 

ggplot(dataudemy, 
       aes(x=is_paid, 
           y=num_lectures)) + 
  geom_boxplot()

ggplot(data = dataudemy, 
       aes(x = num_reviews, 
           y = num_lectures, 
           col = is_paid)) +
  geom_point() + geom_smooth()
```

### Tests

# Is the average price paid for courses different from 40? 

```{r}
t.test(dataudemy$price,
       mu = 40)
```
#Are the average number of subscribers and the number of reviews equal to each other? 

```{r}
t.test(x = dataudemy$num_subscribers, 
       y = dataudemy$num_reviews)
```

#Is there any difference between the average price for different levels?
```{r}
ggplot(dataudemy, 
       aes(x = level, 
           y = price, fill = level)) +
    geom_boxplot() +
  ggtitle("Boxplot of Price for Level")+
  xlab("Level ")+
  ylab(" Price")
```
```{r}
onetestanova <- aov(price ~ level, dataudemy)
summary(onetestanova)
```





##Simple Linear regression
##RQ
##Is there a relationship between the number of lectures and the number of reviews for udemy courses?
```{r}
model <- lm(num_lectures~num_reviews, 
            data=udemy)
summary(model)
```

### Scatter Plot
```{r}
ggplot(udemy, 
       aes(x=num_reviews, 
           y=num_lectures)) + 
  geom_point() + 
  stat_smooth(method = lm)
```

#Normality Check
```{r}
qqnorm(model$residuals)
qqline(model$residuals)
```

```{r}
shapiro.test(udemy$num_lectures)
```

## Residuals vs Fitted Plot
```{r}
yhat=predict(model)
resid=model$residuals

plot(yhat,
     resid,
     pch=16,
     xlab="fitted values",
     ylab="residuals")
abline(h=0)  
```

## Box-Cox Transformation
```{r}
boxcox(model)  
```

apply log(y) transformation


# New model
```{r}
new_model <- lm(log(num_lectures)~num_reviews, 
                data=udemy)
summary(new_model)

ggplot(udemy, 
       aes(x=num_reviews, 
           y=log(num_lectures))) + 
  geom_point() + 
  stat_smooth(method = lm)
```


```{r}
shapiro.test(log(udemy$num_lectures))
```

# Transformation on X
```{r}
new_model <- lm(log(num_lectures)~sqrt(num_reviews), 
                data=udemy)

ggplot(udemy, 
       aes(x=sqrt(num_reviews), 
                  y=log(num_lectures))) + 
  geom_point() + 
  stat_smooth(method = lm)

summary(new_model)

```










##Multiple Linear Regression
##RQ
# Does the number of subscribers, course price, number of reviews, content duration and does money paid for courses or not affect the number of lectures?
  
```{r}
modeludemy <- lm(num_lectures~ num_subscribers+
                  price+
                  num_reviews+
                  content_duration+
                  is_paid,
                dataudemy)

summary(modeludemy) 
```

# QQ-Plot and Normality Test
```{r}
qqnorm(modeludemy$residuals)
qqline(modeludemy$residuals)
shapiro.test(dataudemy$num_lectures)
```

# Box-cox transformation
```{r}
boxcox(modeludemy)

boxcoxnc(dataudemy$num_lectures)
```

# Transformed model
```{r}
modeludemy_transformed <- lm(log(num_lectures)~ num_subscribers+
                   price+
                   num_reviews+
                   content_duration+
                   is_paid,
                 dataudemy)

summary(modeludemy_transformed)
```

# QQ-Plot and Normality Test
```{r}
qqnorm(modeludemy_transformed$residuals)
qqline(modeludemy_transformed$residuals)
shapiro.test(log(dataudemy$num_lectures))
```

# Variance Infilation Factor Check
```{r}
vif(newmodel_udemy_transformed)
```

# Residuals disrribution
```{r}
yhat=predict(newmodel_udemy_transformed)
resid=newmodel_udemy_transformed$residuals
plot(yhat,
     resid,
     pch=16,
     xlab="fitted values",
     ylab="residuals")
abline(h=0)
```

#Linearity Check
```{r}
plot(log(num_lectures)~num_subscribers,data = dataudemy)
plot(log(num_lectures)~price,data = dataudemy)
plot(log(num_lectures)~content_duration,data = dataudemy)

par(mfrow=c(2,2))
plot(newmodel_udemy_transformed)
```

#The best version of the model
```{r}
newmodel_udemy_transformed <- lm(log(num_lectures)~ num_subscribers+ 
                                   price+ 
                                   content_duration,
                                 dataudemy)

summary(newmodel_udemy_transformed)
```


```{r}
```



